Bayes Optimal Informer Sets for Drug Discovery\thanks{abc}

### 2020-04-02 BOISE/Paper_draft/draft.tex
fix formula reference

\begin{equation}\label{eq:thresh}
x_{ij} = \begin{cases}
		1, &\text{ if }
	      z_{ij} \geq \mbox{mean}[z_{i\cdot}] + 2 \times \mbox{s.d.}[z_{i\cdot}],\\
		0 & \text{ if }
	      z_{ij} < \mbox{mean}[z_{i\cdot}] + 2 \times \mbox{s.d.}[z_{i\cdot}].
	\end{cases}
\end{equation}
Throughout the paper we will use (Eq. \ref{eq:thresh}) to binarize target outcomes.

>>>>

\begin{eqnarray}
\label{eq:thresh}
x_{ij} = \begin{cases}
		1, &\text{ if }
	      z_{ij} \geq \mbox{mean}[z_{i\cdot}] + 2 \times \mbox{s.d.}[z_{i\cdot}],\\
		0 & \text{ if }
	      z_{ij} < \mbox{mean}[z_{i\cdot}] + 2 \times \mbox{s.d.}[z_{i\cdot}].
	\end{cases}
\end{eqnarray}
Throughout the paper we will use (Eq. \ref{eq:thresh}) to binarize target outcomes.
